We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2017-11-04 paper/paper.tex
abstract

\begin{abstract}
In this paper we quantify the asphericity in the spatial distribution of the
brightest satellites around the Milky Way (MW) and M31, the dominant
galaxies in the Local Group (LG).
We use the Illustris-1 and ELVIS simulations to quantify asphericity
in the Lambda Cold Dark Matter paradigm.  
We build explicit probability distributions of
finding an aspherical satellite distribution, allowing for an easy
reproducibility of the results presented here and a standarized method
to compare probability distributions derived from different
simulations. 
We estimate that only $0.05\%$ to $0.25\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of deviation from
sphericity.
This makes the LG a $3\sigma$ outlier, with all the weight lying on
the extremly planar MW satellite distribution.

>>>>

\begin{abstract}
Here we quantify the asphericity in the spatial distribution of the
brightest satellites around the Milky Way (MW) and M31, the dominant
galaxies in the Local Group (LG).
We use the Illustris-1 and ELVIS simulations to quantify asphericity
in the Lambda Cold Dark Matter paradigm.  
We build explicit probability distributions of
finding an aspherical satellite distribution, allowing for an easy
reproducibility of the results presented here and a standarized method
to compare probability distributions derived from different
simulations. 
We estimate that only $0.05\%$ to $0.25\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of deviation from
sphericity.
This makes the LG a $3\sigma$ outlier, with all the weight lying on
the extremly planar MW satellite distribution.
